### 2018-02-17 doc/manuscript.Rmd
setup and caption chunks as one

```{r setup, message=FALSE, echo=FALSE}
devtools::load_all('.')
library(ggplot2)
library(patchwork)
library(dplyr)
knitr::opts_chunk$set(echo = FALSE)
ds0yr <- project_data %>% 
    filter(VN == 0)
```

```{r caption_setup}
## Include captions below using `captioner` package
fig <- captioner::captioner(prefix = 'Figure')
cite_f <- pryr::partial(fig, display = 'cite')
sfig <- captioner::captioner(prefix = 'Supplemental Figure')
cite_sf <- pryr::partial(sfig, display = 'cite')

>>>>

```{r setup, message=FALSE, echo=FALSE}
devtools::load_all('.')
library(ggplot2)
library(patchwork)
library(dplyr)
knitr::opts_chunk$set(echo = FALSE)
ds0yr <- project_data %>% 
    filter(VN == 0)

## Include captions below using `captioner` package
fig <- captioner::captioner(prefix = 'Figure')
cite_f <- pryr::partial(fig, display = 'cite')
sfig <- captioner::captioner(prefix = 'Supplemental Figure')
cite_sf <- pryr::partial(sfig, display = 'cite')
